Women in Film

### 2017-07-16 draft_post.Rmd
Working on just writers

gender <- read_csv("gender.csv") %>%
    filter(important == "1",
           gender != "NULL")

@@

## Impact of producers, writers, and directors

*Rough mockup for viz of writer/director viz*

@@

she_gender_ratio <- pronoun_imdb %>%
    inner_join(gender, by = "imdb") %>% ## to get gender of writers, etc
    filter(word1 == "she",
           str_detect(word2, "[a-z]+"),
           nchar(word2) > 2) %>%
    group_by(word2) %>%
    mutate(total = n_distinct(scriptID)) %>%
    ungroup %>%
    count(gender, word2, total) %>%
    spread(gender, n, fill = 0) %>%
    mutate(female = (female + 1) / sum(female + 1),
           male = (male + 1) / sum(male + 1),
           she_ratio = female / male,
           she_logratio = log2(she_ratio)) %>%
    arrange(desc(she_logratio))

@@

she_gender_ratio %>%
    select(word2, she_ratio, she_logratio, she_total = total) %>%
    left_join(he_gender_ratio %>%
                  select(word2, he_ratio, he_logratio, he_total = total)) %>%
    top_n(300, she_total) %>%
    ggplot(aes(she_logratio, he_logratio, label = word2,
               size = (she_total + he_total),
               color = she_ratio / he_ratio)) +
    annotate("text", x = 0.8, y = 0.8,
             label = "Male and female creators\ndescribing women",
             family = "RobotoCondensed-Regular") +
    annotate("text", x = -0.8, y = -0.8,
             label = "Male and female creators\ndescribing men",
             family = "RobotoCondensed-Regular") +
     annotate("text", x = 0.8, y = -0.8,
             label = "Female creators describing women\nMale creators decribing men",
             family = "RobotoCondensed-Regular") +
     annotate("text", x = -0.8, y = 0.8,
             label = "Female creators describing men\nMale creators decribing women",
             family = "RobotoCondensed-Regular") +
   geom_vline(xintercept = 0, color = "gray50", lty = 2, size = 1.5) +
    geom_hline(yintercept = 0, color = "gray50", lty = 2, size = 1.5) +
    geom_text(family = "RobotoCondensed-Regular", size = 3, 
              vjust = 1.2, hjust = 1.2,
              check_overlap = TRUE) +
    geom_point(alpha = 0.5) +
    theme_void() +
    scale_y_continuous(limits = c(-1.1, 1.1)) +
    scale_x_continuous(limits = c(-1.1, 1.1)) +
    scale_color_viridis(end = 0.8) +
    theme(legend.position="none")

@@

>>>>

gender <- read_csv("gender.csv") %>%
    filter(important == "1",
           gender != "NULL",
           role == "writer")

@@

## Impact of writers

*Rough mockup for viz of writer viz*

@@

she_gender_ratio <- pronoun_imdb %>%
    inner_join(gender, by = "imdb") %>% ## to get gender of writers
    filter(word1 == "she",
           str_detect(word2, "[a-z]+"),
           nchar(word2) > 2) %>%
    group_by(word2) %>%
    mutate(total = n_distinct(scriptID)) %>%
    ungroup %>%
    count(gender, word2, total) %>%
    spread(gender, n, fill = 0) %>%
    mutate(female = (female + 1) / sum(female + 1),
           male = (male + 1) / sum(male + 1),
           she_ratio = female / male,
           she_logratio = log2(she_ratio)) %>%
    arrange(desc(she_logratio))

@@

she_gender_ratio %>%
    select(word2, she_ratio, she_logratio, she_total = total) %>%
    left_join(he_gender_ratio %>%
                  select(word2, he_ratio, he_logratio, he_total = total)) %>%
    top_n(300, she_total) %>%
    ggplot(aes(she_logratio, he_logratio, label = word2,
               size = (she_total + he_total),
               color = she_ratio / he_ratio)) +
    annotate("text", x = 0.8, y = 0.8,
             label = "Male and female writers\ndescribing women",
             family = "RobotoCondensed-Regular") +
    annotate("text", x = -0.8, y = -0.8,
             label = "Male and female writers\ndescribing men",
             family = "RobotoCondensed-Regular") +
     annotate("text", x = 0.8, y = -0.8,
             label = "Female writers describing women\nMale writers decribing men",
             family = "RobotoCondensed-Regular") +
     annotate("text", x = -0.8, y = 0.8,
             label = "Female writers describing men\nMale writers decribing women",
             family = "RobotoCondensed-Regular") +
   geom_vline(xintercept = 0, color = "gray50", lty = 2, size = 1.5) +
    geom_hline(yintercept = 0, color = "gray50", lty = 2, size = 1.5) +
    geom_text(family = "RobotoCondensed-Regular", size = 3, 
              vjust = 1.2, hjust = 1.2,
              check_overlap = TRUE) +
    geom_point(alpha = 0.5) +
    theme_void() +
    scale_y_continuous(limits = c(-1.1, 1.1)) +
    scale_x_continuous(limits = c(-1.1, 1.1)) +
    scale_color_viridis(end = 0.8) +
    theme(legend.position="none")

@@

Add bar plot for just how women are portrayed
